XXX

### 2012-02-20 paper/engNERwiki.tex
Filtering next...

Strictly speaking, our original assumption of equating Wikipedia articles with named entities is not valid: many pages describe common nouns (Book, Aircraft), numbers (1, 42), currencies (Euro, Dollar) or other concepts that fall outside the scope of NER. In this section, we describe the measures taken to avoid errors introduced by these false entities.

Links to number pages are filtered by the surface form of the page title. To Common nouns are filtered by their surface form and POS category: links that contain no proper nouns are discarded

Proper entities However, such entities are either missing from DBpedia altogether, or we can map the classes they belong to to the NER category \texttt{0} (not an entity). This "ontological filtering" ensures that

Dates require special attention because

Wikipedia 
% Numbers, years.

>>>>

Strictly speaking, our original assumption of equating Wikipedia articles with named entities is not valid: many pages describe common nouns (Book, Aircraft), numbers (1, 42), currencies (Euro, Dollar) or other concepts that fall outside the scope of NER. In this section, we describe the measures taken to avoid errors introduced by these false entities. We shall modify the two approaches -- precision and recall-oriented -- accordingly.

Proper entities that are not deemed NE by ConLL cause XXX little concern: they are either missing from DBpedia altogether, or we can map the classes they belong to to the NER category \texttt{0} (not an entity). This "ontological filtering" ensures that we need no adjustment XXX to our original method.

Links to number and common noun pages are handled differently by the two approaches. The precision-oriented method treats them similarly to links to unknown entities and discards the sentences in which they occur. The recall-oriented approach tries to distinguish them from links to entities so that otherwise valid training sentences can be retained XXX. The method is as follows XXX.
\begin{itemize}
\item Common nouns are filtered by POS category: links that contain no proper nouns are ignored.
\item Numbers behave more like proper nouns in that they can refer to entities, such as 737 to the Boeing 737. Therefore, links to number pages are filtered by the surface form of the page title.
\end{itemize}

Time expressions require special attention due to two reasons. First, Wikipedia has pages for years, months and concrete dates, therefore our algorithm might mistake them for entities. Second, as dates are made up of numbers and proper nouns, they can be mistaken for unmarked entities. To avoid these errors, we have create a set of regular expressions that recognize dates and time expressions and changed the recall-oriented method to not treat them as entities.
